Forecasting biodiversity in breeding birds using best practices

### 2017-12-09 manuscript/reviewer_reply.Rmd

*Fig. 6 caption: “compoonents”*

>Thank you for pointing out this error. We have fixed it

*466: only other mention of future forecasts… not sure why this is included in this paper.*

> Thank you again for pointing out that we were unclear here. The purpose of the future forecasts is now explained on lines [[xx]] and [[xx]].

### 2017-12-09 manuscript/reviewer_reply.Rmd

>The definition of hindcasting varies by field. We use it here as it's used in meteorology, where any prediction of observations already available is generally a hindcast, and forecasts are only for predictions which are actually in the future. See Jolliffe & Stephenson 2003 (in manuscript) section 1.4.2 for a longer discussion. We've clarified this in the text.

*25-29: rather than relay the type of information that the paper will provide, the authors should summarize their results and findings*

*57-58: this is not the definition of hindcasting. This is the definition of testing. Also, the authors exclude the many deeper-time hindcasting studies that have been performed on these types of models*

>See comment above on hindcasting. We agree that studies evaluating models using fossil records are an important aspect of this field of research and have included several references for them.

### 2017-12-09 manuscript/draft.Rmd
reply about deep time studies

Despite the emerging interest in forecasting species richness and other aspects
of biodiversity [@jetz2007; @thuiller2011], little is known about how
effectively we can anticipate these dynamics. This is due in part to the long
time scales over which many ecological forecasts are applied [and the resulting
difficulty in assessing whether the predicted changes occurred; @dietze2016].
What we do know comes from a small number of hindcasting studies, where models
are built using data on species occurrence and richness from the past and
evaluated on their ability to predict contemporary patterns [e.g., @algar2009;
@distler2015]. These studies are a valuable first step, but lack several
components that are important for developing forecasting models with high
predictive accuracy, and for understanding how well different methods can
predict the future. These "best practices" for effective forecasting and
evaluation (Box 1) broadly involve: 1) expanding the use of data to include
biological and environmental time-series [@tredennick2016]; 2) accounting for
uncertainty in observations and processes, [@harris2015; @yu2010]; and 3)
conducting meaningful evaluations of the forecasts by hindcasting, archiving
short-term forecasts, and comparing forecasts to baselines to determine whether
the forecasts are more accurate than assuming the system is basically static
[@perretti2013].

>>>>

Despite the emerging interest in forecasting species richness and other aspects
of biodiversity [@jetz2007; @thuiller2011], little is known about how
effectively we can anticipate these dynamics. This is due in part to the long
time scales over which many ecological forecasts are applied [and the resulting
difficulty in assessing whether the predicted changes occurred; @dietze2016].
What we do know comes from a small number of biodiversity studies, where models
are built using data on species occurrence, richness, or community composition
from distinct timeperiods and evaluated on their ability to predict contemporary
[@algar2009; @distler2015] or historic [@maguire2016; @blois2013] patterns.
These studies are a valuable first step, but lack several components that are
important for developing forecasting models with high predictive accuracy, and
for understanding how well different methods can predict the future. These "best
practices" for effective forecasting and evaluation (Box 1) broadly involve: 1)
expanding the use of data to include biological and environmental time-series
[@tredennick2016]; 2) accounting for uncertainty in observations and processes,
[@harris2015; @yu2010]; and 3) conducting meaningful evaluations of the
forecasts by hindcasting, archiving short-term forecasts, and comparing
forecasts to baselines to determine whether the forecasts are more accurate than
assuming the system is basically static [@perretti2013].
